Simulating High-Dimensional Multivariate Data

### 2020-12-29 index.Rmd
Update code to bigsimr_0.9.3

```{r serveHelper, include=FALSE, eval=FALSE}
## rmote::start_rmote()
## library(ggplot2); qplot(mpg, wt, data=mtcars, colour=cyl)
## bookdown::render_book("index.Rmd", "bookdown::pdf_book", output_dir = "pdf")
## bookdown::preview_chapter("index.Rmd")
bookdown::serve_book()
```

>>>>

```{r serveHelper, include=FALSE, eval=FALSE}
## rmote::start_rmote()
## library(ggplot2); qplot(mpg, wt, data=mtcars, colour=cyl)
## bookdown::render_book("index.Rmd", "bookdown::pdf_book", output_dir = "pdf")
## bookdown::preview_chapter("index.Rmd")
rmarkdown::render_site(encoding = 'UTF-8')
bookdown::serve_book()
```
